Bare Demo of IEEEtran.cls for Journals

### 2019-12-10 2-oracle/report/paper.tex
write introduction and related work part

\section{Introduction}
\IEEEPARstart{T}{his}

@@

In order to construct a template, the intuition is to take all the samples of one category and take the average. However, we observe that the samples of the same character may have different size and position in the box. So the template generated by the above procedure may be blur and unrepresentative. Therefore, we preprocess the samples to find the best focus and scale. First find the center of mass of the box, which is analogous to the same term in physics. We denote the gray scale image as $G$. Consider the blackness as a measure of intensity, so we take the complement image of $G$, denoted as $\hat{G}$. i.e. $\hat{G}(i,j)=255-G(i,j)$. Then we can calculate the center of mass by the following formula:
\begin{align*}
	c_x=\frac{\sum_{i,j}\hat{G}(i,j)\cdot i}{\sum_{i,j} \hat{G}(i,j)}\\
	c_y=\frac{\sum_{i,j}\hat{G}(i,j)\cdot j}{\sum_{i,j} \hat{G}(i,j)}
\end{align*}

@@

To measure the similarity of a sample and a template, we think of two metrics, normed mean square error and normed correlation, which is defined below:
\begin{align*}
	\text{NMSE}(G',T)= \frac{\sum_{x,y} (T(x,y)-G'(x,y))^2}{\sqrt{\sum_{x,y}T(x,y)^2 \cdot \sum_{x,y} G'(x,y)^2}}\\
	\text{NCOR}(G',T)= \frac{\sum_{x,y} (T(x,y) \cdot G'(x,y))}{\sqrt{\sum_{x,y}T(x,y)^2 \cdot \sum_{x,y} G'(x,y)^2}}
\end{align*}

@@

% ljy
\subsection{Ensemble of Two Methods}

@@

We first obtain the grey scale version of the images.
For the test on the neural network, we normalize images as before and set pixels with values less than some threshold $\delta$ to 0.
For the test on the template matching, we do not normalize images but set pixels with values less than some threshold $\Delta$ to 0.
In this way, we can remove the influence of the background color on the recognition result.

\begin{table}[h]
	\centering
	\caption{Accuracy for Different Models}
	\label{tab:result}
	\begin{tabular}{|c|c|c|}
		\hline
		& Cat10 & Cat40 \\\hline
		DNN ($\delta=0.5$) & 0.8475 & 0.5275 \\\hline
		DNN Ensemble ($\delta=0.5$) & 0.8000 & 0.56 \\\hline
		TM ($\Delta=?$) & ? & ? \\\hline
		TM Ensemble ($\Delta=?$) & ? & ? \\\hline
	\end{tabular}
\end{table}

>>>>

\section{Introduction}
\IEEEPARstart{O}{racle} bone script is the earliest known Chinese writing, which dates back to the late 2nd millennium BC. Detection and recognition of oracle bone script is crucial for the understanding of the social and political characteristics of ancient Chinese. It is also significant in education and arts nowadays, as the script is a cultural heritage of both China and the human civilization.

In this paper, we propose different methods to detect hand-written oracle bone script, which facilitates interactive applications. We try both the traditional template matching and the convolutional neural network. We also make an ensemble of the two methods to get a better performance.

\section{Related Work}
Though not been widely researched, Lin \cite{ssd} uses Single Shot Multibox Detector (SSD) to detect oracle bone inscription and receives considerable results.

@@

In order to construct a template, the intuition is to take all the samples of one category and take the average. However, we observe that the samples of the same character may have different size and position in the box. So the template generated by the above procedure may be blur and unrepresentative. Therefore, we preprocess the samples to find the best focus and scale. First find the center of mass of the box, which is analogous to the same term in physics. We denote the gray scale image as $G$. Consider the blackness as a measure of intensity, so we take the complement image of $G$, denoted as $\hat{G}$. i.e. $\hat{G}(i,j)=255-G(i,j)$. Then we can calculate the center of mass by the following formula:
\begin{align*}
	c_x=\frac{\sum_{i,j}\hat{G}(i,j)\cdot i}{\sum_{i,j} \hat{G}(i,j)} \\
	c_y=\frac{\sum_{i,j}\hat{G}(i,j)\cdot j}{\sum_{i,j} \hat{G}(i,j)}
\end{align*}

@@

To measure the similarity of a sample and a template, we think of two metrics, normed mean square error and normed correlation, which is defined below:
\begin{align*}
	\text{NMSE}(G',T)= \frac{\sum_{x,y} (T(x,y)-G'(x,y))^2}{\sqrt{\sum_{x,y}T(x,y)^2 \cdot \sum_{x,y} G'(x,y)^2}} \\
	\text{NCOR}(G',T)= \frac{\sum_{x,y} (T(x,y) \cdot G'(x,y))}{\sqrt{\sum_{x,y}T(x,y)^2 \cdot \sum_{x,y} G'(x,y)^2}}
\end{align*}

@@

% ljy
\subsection{Ensemble of Two Methods}
To improve the performance of the model, we add an ensemble network for CNN and template matching. It takes the output of CNN and template matching as input, and through a linear regression, produces the score of each class.

@@

We first obtain the grey scale version of the images.
For the test on the neural network, we normalize images as before and set pixels with values less than some threshold $\delta$ to 0.
For the test on the template matching, besides the normalization, we also set pixels with values less than some threshold $\Delta$ to 0.
In this way, we can remove the influence of the background color on the recognition result.

\begin{table}[h]
	\centering
	\caption{Accuracy for Different Models}
	\label{tab:result}
	\begin{tabular}{|c|c|c|}
		\hline
		                            & Cat10  & Cat40  \\\hline
		DNN ($\delta=0.5$)          & 0.8475 & 0.5275 \\\hline
		DNN Ensemble ($\delta=0.5$) & 0.8000 & 0.56   \\\hline
		TM ($\Delta=150$, NMSE)     & 0.7775 & 0.6325 \\\hline
		TM ($\Delta=150$, NCCOR)    & 0.8000 & 0.6500 \\\hline
		TM Ensemble ($\Delta=?$)    & ?      & ?      \\\hline
	\end{tabular}
\end{table}
